\documentclass{article}
\usepackage{iclr2026_conference,times}
\input{math_commands.tex}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\title{Task Planning Under Contact Uncertainty: ICLR Main-Conference Gate Archive}
\author{Anonymous Authors}
\begin{document}
\maketitle
\begin{abstract}
This document is not an ICLR main-conference submission. It is the v3 main-conference gate for a generated robotics draft about task and motion planning. The original research bet was: Plan over uncertainty in future contact modes rather than over abstract symbolic preconditions. After a stricter hostile review, the honest terminal decision is \textbf{KILL/ARCHIVE}. Submission-hardening version: v3.
\end{abstract}

\section{Gate Decision}
The v2 paper was workshop-only. Under the active ICLR-main standard, that is insufficient. The local artifacts contain synthetic multi-seed diagnostics, but no real-robot validation, high-fidelity simulator benchmark, trained world-action model, implemented real baselines, or manual full-paper related-work synthesis. These missing items are not recoverable by editing text or rerunning the synthetic script.

\section{Fatal ICLR-Main Blockers}
\begin{itemize}
\item Evidence is synthetic and generated from a shared batch template.
\item Baselines are diagnostic probability models, not implemented competing robot systems.
\item Ablations do not correspond to a trained model checkpoint.
\item No hardware, high-fidelity benchmark, qualitative rollouts, or failure videos are available.
\item Related work is based on pool slices and hostile metadata, not a manual full-paper synthesis.
\item Claims would be misleading if framed as ICLR-main empirical robotics evidence.
\end{itemize}

\section{Hostile Prior-Work Pressure}
The closest local hostile records include:
\begin{itemize}
\item From Classical Planning to Learning-Based Task and Motion Planning: A Survey of Intelligent Planning Systems (n.d.)
\item Motion Planning of Multi-Limbed Robots Subject to Equilibrium Constraints: The Free-Climbing Robot Problem (2006)
\item Recent Trends in Task and Motion Planning for Robotics: A Survey (2023)
\item Contingent Task and Motion Planning under Uncertainty for Human-Robot Interactions (2020)
\item SCU-T-MPC: Risk-Aware and Socially Compliant Topological Motion Planning Under Uncertainty (2026)
\end{itemize}
These works make generic world models, uncertainty, model-based planning, and robot policy robustness crowded. Without real empirical evidence, the remaining novelty boundary is too weak for ICLR main.

\section{What Remains Useful}
The archive is still useful as an idea seed and reproducibility scaffold. The synthetic code, stress-test CSVs, reviewer attacks, and novelty-boundary docs can inform a future project. The correct next step is not more paper polishing; it is new evidence: implemented models, real baselines, manual related work, and robot or high-fidelity simulator validation.

\section{Terminal Action}
Decision: \textbf{KILL/ARCHIVE for ICLR main}. Do not submit this paper to ICLR main in the current form. Revival requires a substantially new empirical project.

\end{document}
